---
title: "WSR Hour of code Challenge"
author: "Klinkenberg"
output: html_document
---

<iframe width="280" height="157" style="float:right;" src="https://www.youtube.com/embed/FC5FbmsH4fw" frameborder="0" allow="accelerometer; autoplay; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>

Between 3-9 dec, ten percent of students around the world will celebrate Computer Science Education Week by doing an [Hour of Code](https://hourofcode.com/nl) at their school. It’s an opportunity for every student to learn how the technology around us works.

### Join this weeks WSR hour of code challenge 

just for the fun of it!

Let's do this. I challenge you to do this in one hour.

We have been talking about validity and reliability. Try to code the image below and make it so that you can modify the amount of [precision and accuracy](https://en.wikipedia.org/wiki/Accuracy_and_precision) You don't have to animate it. Be creative!

```{r, echo=FALSE, fig.show='animate', ffmpeg.format='gif', dev='jpeg', interval=.2, message=FALSE, warning=FALSE, fig.height=2}
# target practice
# install.packages("plotrix")
library("plotrix")

for(i in 1:30) {

par(mar = c(0,0,0,0))  
  
plot(-4:4,-4:4,
     type = "n",
     xlab = "",
     ylab = "",
     main = "",
     xaxt = "n", 
     yaxt = "n")

# Draw target
draw.circle(0,0, 3.5, border= "black")
draw.circle(0,0, 2.5, border= "blue",
                      col   = "blue")
draw.circle(0,0, 1.5, border= "red", 
                      col   = "red")
draw.circle(0,0,  .5, border= "yellow", 
                      col   = "yellow")

# shoot
n           = 10  # how many times to shoot
imprecision = runif(1,0,1)  # how imprecise do we shoot
inaccuracy  = runif(1,0,1)  # how inacurate do we shoot

x = rnorm(n,0,imprecision) +
    rnorm(1,0,inaccuracy)
y = rnorm(n,0,imprecision) +
    rnorm(1,0,inaccuracy)

lines(x,y, type="p", col="black", lwd=4)

}
```

Now turn up [Can't Hold Us (feat. Ray Dalton)](https://open.spotify.com/track/31qgVdvSqTQ7unwQQngycB?si=YonS10zVRsKRkcNcHgOD3A) and make it happen.

Here are some usefull packages and functions you could use.

```{r, eval=FALSE}
# Package plotrix for making nice circles
install.packages("plotrix")
library("plotrix")
draw.circle()

# Base R
rnorm()
plot()
lines()
```

When your done, let us know what you have created. 

Have Fun,
<br>Sharon & Roeland